|

### 2021-03-14 documentation/userguide.Rmd
Amended documentation to apply to the package and not the dataset

---
title: |
  | PollBasePro v`r packageVersion("BritPol")` (Beta)
  | User Guide and Codebook
date: |
  | This version: `r stringr::str_remove(format(Sys.time(), "%d %B %Y"), "^0")`
indent: yes
fontsize: 12pt
geometry: margin = 1.15in
subparagraph: yes
compact-title: false
bibliography: _assets/master.bib
biblio-style: _assets/apsr.bst
classoption: a4paper
output: 
  bookdown::pdf_document2: 
    latex_engine: xelatex
    toc: false
    keep_tex: false
    includes:
      in_header:
        - _assets/cb-preamble.tex
    number_sections: false
    fig_caption: true
---

@@

library(PollBasePro)
library(kableExtra)
library(tidyverse)
library(lubridate)
library(brms)
library(here)

@@

# About PollBasePro

PollBasePro is a data package for the `R` programming language. It includes two datasets: `pollbase` and `pollbasepro`. The first provides a long-format and ready-to-analyse version of Mark Pack's [-@pack2021] dataset of historic British public opinion polls combined with more recent polling data from Wikipedia. The second provides `r format(nrow(pollbasepro), big.mark = ",")` daily estimates of voting intention figures for each of Britain's three largest parties between `r str_remove(format(min(pollbasepro$date), "%d %B %Y"), "^0")` and `r str_remove(format(max(pollbasepro$date), "%d %B %Y"), "^0")`.

Both `pollbase` and `pollbasepro` are *living datasets*. Thus, users should endeavour to use only the most recent version of the data when conducting their analyses. This will become more important in the future, as we intend to add new polls and estimates over time. Likewise, we cannot rule out that minor mistakes might have crept into our data processing pipeline. To guard against this, we have made all of our materials available for others to inspect. If you find an error in the code or wish to make a recommendation for a future update, we invite you to raise an issue on the PollBasePro GitHub repository.

# Citing PollBasePro

If you use PollBasePro, you should also cite it. This is good practice and also allows the PollBasePro team to monitor how the data have been used. The project comprises three items: the data, this user guide, and a companion paper. The citations for each item are as follows:

@@

- **Documentation:** Bailey, J., M. Pack, and L. Mansillo (`r format(Sys.Date(), format = "%Y")`) PollBasePro v`r packageVersion("BritPol")`: User Guide and Codebook. Retrieved from doi.

@@

# Using PollBasePro

Getting started with PollBasePro in `R` is simple. It requires only three short steps: first, to install the package; second, to load the package; and, third, to load the data. Once you have taken these three steps, you can then begin analysing the data. Note that PollBasePro is not yet available on CRAN, the service that hosts most `R` packages. As such, it is not yet possible to install PollBasePro with `R`'s standard `install.packages()` function. Instead, we must install it directly from its GitHub repository. Thankfully this is straightforward and requires only that you run the following code in your `R` console:

```{r install-pbp, eval = FALSE}
# 1. Install the PollBasePro package from GitHub
devtools::install_github("jackobailey/PollBasePro")

# 2. Load the PollBasePro package in R
library(PollBasePro)

@@

Though PollBasePro is first and foremost an `R` data package, we have sought to accommodate those who use Stata and SPSS too. To make this as easy as possible, we have made both the `pollbase` and `pollbasepro` datasets available as .dta and .sav files. These include all necessary value and variable labels and should work seamlessly with both software packages. You can download the latest version of the data by clicking the links below:

@@

For the sake of openness and transparency, we provide a change log that lists all updates and changes made to the PollBasePro datasets and documentation over time. If you think that you have found a problem with either, please raise an issue on the project's GitHub repository.

>>>>

---
title: |
  | BritPol v`r packageVersion("BritPol")` (Beta)
  | User Guide and Data Codebook
date: |
  | This version: `r stringr::str_remove(format(Sys.time(), "%d %B %Y"), "^0")`
indent: yes
fontsize: 12pt
geometry: margin = 1.15in
subparagraph: yes
compact-title: false
bibliography: _assets/master.bib
biblio-style: _assets/apsr.bst
classoption: a4paper
output: 
  bookdown::pdf_document2: 
    latex_engine: xelatex
    toc: false
    keep_tex: false
    includes:
      in_header:
        - _assets/cb-preamble.tex
    number_sections: false
    fig_caption: true
---

@@

library(BritPol)
library(kableExtra)
library(tidyverse)
library(lubridate)
library(brms)
library(here)

@@

# About BritPol

BritPol is a data package for the `R` programming language. It includes two datasets: `pollbase` and `pollbasepro`. The first provides a long-format and ready-to-analyse version of Mark Pack's [-@pack2021] dataset of historic British public opinion polls combined with more recent polling data from Wikipedia. The second provides `r format(nrow(pollbasepro), big.mark = ",")` daily estimates of voting intention figures for each of Britain's three largest parties between `r str_remove(format(min(pollbasepro$date), "%d %B %Y"), "^0")` and `r str_remove(format(max(pollbasepro$date), "%d %B %Y"), "^0")`.

Both `pollbase` and `pollbasepro` are *living datasets*. Thus, users should endeavour to use only the most recent version of the data when conducting their analyses. This will become more important in the future, as we intend to add new polls and estimates over time. Likewise, we cannot rule out that minor mistakes might have crept into our data processing pipeline. To guard against this, we have made all of our materials available for others to inspect. If you find an error in the code or wish to make a recommendation for a future update, we invite you to raise an issue on the BritPol GitHub repository.

# Citing the Data

If you use the `pollbasepro` data, you should also cite it. This is good practice and also allows us monitor how the data have been used. The `pollbasepro` project comprises three items: the data, this user guide, and a companion paper. The citations for each item are as follows:

@@

- **Documentation:** Bailey, J. (`r format(Sys.Date(), format = "%Y")`) BritPol v`r packageVersion("BritPol")`: User Guide and Data Codebook. Retrieved from doi.

@@

# Using BritPol

Getting started with BritPol in `R` is simple. It requires only three short steps: first, to install the package; second, to load the package; and, third, to load the data. Once you have taken these three steps, you can then begin analysing the data. Note that BritPol is not yet available on CRAN, the service that hosts most `R` packages. As such, it is not yet possible to install BritPol with `R`'s standard `install.packages()` function. Instead, we must install it directly from its GitHub repository. Thankfully this is straightforward and requires only that you run the following code in your `R` console:

```{r install-pbp, eval = FALSE}
# 1. Install the BritPol package from GitHub
devtools::install_github("jackobailey/BritPol")

# 2. Load the BritPol package in R
library(BritPol)

@@

Though BritPol is first and foremost an `R` data package, we have sought to accommodate those who use Stata and SPSS too. To make this as easy as possible, we have made both the `pollbase` and `pollbasepro` datasets available as .dta and .sav files. These include all necessary value and variable labels and should work seamlessly with both software packages. You can download the latest version of the data by clicking the links below:

@@

For the sake of openness and transparency, we provide a change log that lists all updates and changes made to BritPol over time. If you think that you have found a problem with either the data, code, or documentation, please raise an issue on the project's GitHub repository.
